Contextual Combinatorial Cascading Bandits

### 2015-12-19 contextual combinatorial cascading bandits.tex
update proof outline of main theorem

@@

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation}
\label{eq:expectation}
\EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. 
We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is,
	for some $k=1,2,\ldots, \abs{\bA_t}$, 
$$
\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$
At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. 
Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t 
	\mid  k \in[\bO_s], 1 \le s<t \}$.

@@

If we define a function $f_{\wedge}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
\begin{align}
&f_{\wedge} : \cS \times [0,1]^E \to [0,1] \nonumber \\
&f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)
 (1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
 \label{eq:functionfstar}
\end{align}
then we have $\br_{\wedge, t} = f_{\wedge}(\bA_t, \bw_t)$ and $\EE[\br_{\wedge, t}] = f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. To simplify notations, we assume 
$$
\gamma_k' = 1 - \gamma_k.
$$
Then it holds that
\begin{equation}
\label{eq:ConDisRelation}
f_{\wedge}(A, w) = 1 - f(A, 1 - w).
\end{equation}
Let 
\begin{align*}
A_{\wedge, t}^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
f_{\wedge, t}^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
\end{align*}
For the conjunctive objective, the goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
$$
R_{\wedge}(T) = \EE\left[\sum_{t=1}^T R_{\wedge}(t, \bA_t)\right].
$$
where $R_{\wedge}(t, A) = f_{\wedge, t}^{\ast} - f_{\wedge}(A, \theta_{\ast}^{\top}x_t)$.

@@

\begin{theorem}[\cite{abbasi2011improved}]
\label{thm:theta_estimate}
Let 
%$$
%\beta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\det(\lambda I)}\right) + 2 \ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}.
%$$
%\wei{I thought the following is simpler. Should we use the following?}
\begin{equation}
\bbeta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}. \label{eq:definebeta}
\end{equation}
Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
\begin{equation}
\label{eq:estimateTheta}
\norm{\hat{\theta}_t - \theta_{\ast}}_{\bV_{t}} \leq \bbeta_{t}(\delta).
\end{equation}
\end{theorem}

@@

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $\theta_*^{\top}x_{t,a}$ is proved in the following lemma.
\begin{lemma}
\label{lem:estimateU}
When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
$$
0 \leq \bU_t(a) - \theta_{\ast}^{\top}x_{t,a} \leq 2\bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}
\begin{proof}
\begin{align*}
\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
&\leq \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
\end{align*}
\end{proof}

@@

\begin{algorithm}
\caption{C$^3$-UCB}
\label{alg:ConComCascade}
\begin{algorithmic}[1]
\STATE {//Initialization}
\STATE {Parameters: $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$}
\STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
\STATE {$\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
%\STATE{}

@@

To state our main theorem, we need some definitions. Let
$$
f_{\wedge}^* = \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
$$
denote the best expected reward of all time under the conjunctive objective.
Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the {\em probability of full
	observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is 
\begin{align*}
&p_{t, A} = \prod_{k=1}^{\abs{A}-1} (1 - \theta_{\ast}^{\top} x_{t, a_k^t}),\\
&p_{\wedge, t, A} = \prod_{k=1}^{\abs{A}-1} (\theta_{\ast}^{\top} x_{t, a_k^t}).
\end{align*}
We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability over all time that an action could have all base arms observed under the disjunctive objective. The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
\begin{theorem}
\label{thm:main}
Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and 
$\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$.
Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
\begin{align}
R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda}\right) \nonumber \\
&=O\left(\frac{d}{p^*} \sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta}\right) \right),
\end{align}
\begin{align}
R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} \nonumber \\
&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^2}\right) } + \sqrt{\lambda}\right) \nonumber \\
&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta}\right) \right).
\end{align}
%where
%\begin{align*}
%C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K} (1 - \gamma_k')^2 \in [1, K].
%\end{align*}
\end{theorem}

\wei{I hided some paragraphs trying to explain the proof here.
	We will re-write a proof outline after revising the proofs.}
\hidetext{
\wei{I do not see the purpose of putting Lemma 4.4 and 4.5 in this section. Perhaps
	they should all be moved to Section 4.3}
\shuai{I think Section 4.3 will probably be put in the appendix. So I sketch a proof of main theorem here. If all the proofs will be kept, then we don't need Lemma 4.4 and 4.5 here.}

To prove Theorem \ref{thm:main}, we could start from estimating $\EE[R(t, \bA_t)|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
\begin{lemma}
\label{lem:DeltaEstimate}
For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
$$
R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
$$
if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
$$
R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \bbeta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}

So if the chosen action $\bA_t$ is not suboptimal, which means
$$
f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t), ~~ f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(\bA_t, \bU_t).
$$
Then we can derive an estimate of $R(t, \bA_t)$ and $R_{\wedge}(t, \bA_t)$, however, in terms of all base arms in $\bA_t$. Only when the learning agent has observed all base arms of $\bA_t$, we can use such an estimate, which means we are able to estimate

\wei{I do not understand the above paragraph and the formula below.}
\shuai{If we choose action of $\bA_t$ instead of $A_t^{\ast}$, then we can know the differece between their expected reward. But the regret is bounded by all base arms in $\bA_t$. Only the observed base arms can be estimated together. So we can only estimate the following formula. I rewrite the following formula and can explain to you later.}
\begin{align*}
&~~\EE_t[R(t, \bA_t)] \\
&= \EE[R(t, \bA_t) \bOne\{R(t, \bA_t) > 0\} \EE[(1/p_{t, \bA_t}) \bOne\{\bO_t \geq \abs{\bA_t}\}|\bA_t] | \cH_t]\\
&= \EE_t[R(t, \bA_t)(1/p_{t, \bA_t}) \bOne\{R(t, \bA_t) > 0, \bO_t \geq \abs{\bA_t}\}],\\
&~~\EE_t[R_{\wedge}(t, \bA_t)] \\
&= \EE_t[R_{\wedge}(t, \bA_t)(1/p_{\wedge, t, \bA_t}) \bOne\{R_{\wedge}(t, \bA_t) > 0, \bO_{\wedge, t} \geq \abs{\bA_t}\}].
\end{align*}

In real problems involved with recommendations, the click rate is a very small number. Thus for the problem with disjunctive objective, $p^*$ is relatively high and can be regarded as a constant. So we have $p_{t, \bA_t} \geq p^*$. For the problem with conjunctive objective, $p_{\wedge, t, \bA_t}$ might be small. Thus we need the following lemma to find a good substitution of $\bA_t$.

%\begin{lemma}
%\label{lem:prefixExist}
%Let $B_k = (\ba_1^t, \ldots, \ba_k^t), k \leq \abs{A}$ be a prefix of $\bA_t$. Then there exists a prefix $\bB_t$ of $\bA_t$ such that
%$$
%p_{\wedge, t, \bB_t} \geq \frac{1}{2} f_{\wedge, t}^* - \gamma_{\abs{\bB_t}}, \qquad R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t).
%$$
%\end{lemma}
From this lemma, we can use the prefix $\bB_t$ to substitue $\bA_t$ because $p_{\wedge, t, \bB_t}$ is large enough and $R_{\wedge}(t, \bB_t)$ will not be too small. Then follow the above deductions, we can get a good estimate for $\EE[R_{\wedge}(t, \bA_t)|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$. Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\bbeta_{t-1}(\delta)$, we can get an estimate for $\EE[R_{\wedge}(t, \bA_t)|\cH_{t-1}]$, thus for $R_{\wedge}(T)$. We leave all details in the next subsection.
}

@@

We first provide a basic property of functions $f$ and $f_{\wedge}$ as defined
in~Eq.\eqref{eq:functionf} and \eqref{eq:functionfstar}.
\begin{lemma}
\label{lem:increasing} 
Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Then $f(A, w)$ and $f_{\wedge}(A, w)$ are increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
$$
f(A, w) \leq f(A, w'), ~~ f_{\wedge}(A, w) \leq f_{\wedge}(A, w').
$$
\end{lemma}
\begin{proof}
Without the loss of generality, we prove for the case
	of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. 
First, for $1 \leq k \leq m$, we have
\begin{align*}
&\gamma_{k} - \sum_{i=k+1}^m \gamma_i \prod_{j = k + 1}^{i - 1} (1 - w_j') w_i'\\
\geq &~\gamma_k [1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
\geq &~\gamma_{k} \cdot 0 = 0.
\end{align*}
Then it implies that
\begin{align*}
&\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
\leq &\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'.\\
\end{align*}
Therefore, 
\begin{align*}
& f(A; w_1, \dots, w_k, w_{k+1}', \dots, w_m')\\
&=\sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
&\qquad \cdot [\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
&\leq \sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
&\qquad \cdot [\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
&=f(A; w_1, \ldots, w_{k-1}, w_{k}', \ldots, w_m').
\end{align*}
By letting $\gamma_k = 1 - \gamma_k'$ and using the relation
	in Eq. \eqref{eq:ConDisRelation}, the increasing property of $f_{\wedge}$ is obtained directly.
\end{proof}

>>>>

\newcommand{\CLemmaPrefixExi}{
	Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
	$$
		p_{\wedge, t, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad R_{\wedge}(t, B) \geq \frac{1}{2} R_{\wedge}(t, A).
	$$ 
}
\newcommand{\CLemmaIncre}{
	Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Then $f(A, w)$ and $f_{\wedge}(A, w)$ are increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
	$$
		f(A, w) \leq f(A, w'), ~~ f_{\wedge}(A, w) \leq f_{\wedge}(A, w').
	$$
}
\newcommand{\CLemmaTech}{
	Suppose $0 \leq \gamma_k, \gamma_k' \leq 1, k \in [K]$. Let $0 \leq w_1, \ldots, w_m \leq 1$, $r_1, \ldots, r_m \geq 0$ and $u_i = \min\{w_i + r_i, 1\}, 1 \leq i \leq m$. Then
	\begin{align*}
		&f(A^{(m)}, u) \leq f(A^{(m)}, w) + \sum_{k=1}^{m} \gamma_k r_k,\\
		&f_{\wedge}(A^{(m)}, u) \leq f_{\wedge}(A^{(m)}, w) + \sum_{k=1}^{m} (1 - \gamma_k') r_k,
	\end{align*}
	where $A^{(m)} = (1, 2, \ldots, m), u = (u_1, \ldots, u_m)$ and $w = (w_1, \ldots, w_m)$.
}
\newcommand{\CLemmaSumXiEstimateInDet}{
	If $\lambda \geq C_\gamma$, then
	$$
	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
	$$
}
\newcommand{\CLemmaDetVt}{
	$\det(\bV_t)$ is increasing with respect to $t$ and 
	$$
		\det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
	$$
}

@@

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$.
Thus $\cH_t$ contains all information and observations at time $s < t$ and context information at time $t$. Given history $\cH_t$, we assume $\bw_{t,a}$'s are mutually independent and satisfy
\begin{equation} % eq:expectation
	\label{eq:expectation}
	\EE[\bw_{t,a} | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. 
We define random variable $\bO_t$ as the number of observed base arms in $\bA_t$, that is, for some $k=1,2,\ldots, \abs{\bA_t}$, 
$$
	\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
	\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$
At the end of every time $t$, the agent observes the first $\bO_t$ items of $\bA_t$. We say that item $a$ is {\it observed} if $a = \ba_k^t$ for some $k \leq \bO_t$. 
Thus, $\cH_t$ consists of $\{x_s, \bA_s = (\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s),x_t \mid  k \in[\bO_s], 1 \le s<t \}$.

@@

If we define a function $f_{\wedge}$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS, w = (w(1), \ldots, w(L))$ by
\begin{align}
	&f_{\wedge} : \cS \times [0,1]^E \to [0,1] \nonumber \\
	&f_{\wedge}(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_k' \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
	\label{eq:functionfstar}
\end{align}
then we have $\br_{\wedge, t} = f_{\wedge}(\bA_t, \bw_t)$ and $\EE[\br_{\wedge, t}] = f_{\wedge}(\bA_t, \theta_{\ast}^{\top}x_t)$ where $x_t = (x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. To simplify notations, we assume 
$$
	\gamma_k' = 1 - \gamma_k.
$$
Then it holds that
\begin{equation} %eq:ConDisRelation
	\label{eq:ConDisRelation}
	f_{\wedge}(A, w) = 1 - f(A, 1 - w).
\end{equation}
Let 
\begin{align*}
	A_{\wedge, t}^{\ast} &= \argmax_{A\in \cS} f(A,\theta_{\ast}^{\top}x_t),\\
	f_{\wedge, t}^{\ast} &= f(A_t^{\ast}, \theta_{\ast}^{\top}x_t).
\end{align*}
For the conjunctive objective, the goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
$$
	R_{\wedge}(T) = \EE\left[\sum_{t=1}^T R_{\wedge}(t, \bA_t)\right].
$$
where $R_{\wedge}(t, A) = f_{\wedge, t}^{\ast} - f_{\wedge}(A, \theta_{\ast}^{\top}x_t)$.

@@

\begin{theorem}[\cite{abbasi2011improved}] %estimate of theta
	\label{thm:theta_estimate}
	Let 
	\begin{equation}
		\bbeta_{t}(\delta) = \sqrt{\ln\left(\frac{\det(\bV_{t})}{\lambda^d \delta^2}\right)} + \sqrt{\lambda}. \label{eq:definebeta}
	\end{equation}
	Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
	\begin{equation}
		\label{eq:estimateTheta}
		\norm{\hat{\theta}_t - \theta_{\ast}}_{\bV_{t}} \leq \bbeta_{t}(\delta).
	\end{equation}
\end{theorem}

@@

The fact that $\bU_t(a)$ is an upper confidence bound of expected weight $\theta_*^{\top}x_{t,a}$ is proved in the following lemma.
\begin{lemma} %estimate of U
	\label{lem:estimateU}
	When Eq.\eqref{eq:estimateTheta} holds for time $t-1$, we have
	$$
		0 \leq \bU_t(a) - \theta_{\ast}^{\top}x_{t,a} \leq 2\bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
	$$
\end{lemma}
\begin{proof}
	\begin{align*}
		\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_{\ast}^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_{\ast}}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
		&\leq \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
	\end{align*}
\end{proof}

@@

\begin{algorithm} %C^3-UCB algorithm
	\caption{C$^3$-UCB}
	\label{alg:ConComCascade}
	\begin{algorithmic}[1]
		\STATE {//Initialization}
		\STATE {Parameters: $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$}
		\STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
		\STATE {$\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
		%\STATE{}

@@

To state our main theorem, we need some definitions. Let
$$
	f_{\wedge}^* = \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
$$
denote the best expected reward of all time under the conjunctive objective.
Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the {\em probability of full observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is 
\begin{align*}
	&p_{t, A} = \prod_{k=1}^{\abs{A}-1} (1 - \theta_{\ast}^{\top} x_{t, a_k^t}),\\
	&p_{\wedge, t, A} = \prod_{k=1}^{\abs{A}-1} (\theta_{\ast}^{\top} x_{t, a_k^t}).
\end{align*}
We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability over all time that an action could have all base arms observed under the disjunctive objective. The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
\begin{theorem} %main theorem
	\label{thm:main}
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$. Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
	\begin{align}
		R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right),
	\end{align}
	\begin{align}
		R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln \left(\frac{C_\gamma T}{\delta^{2/d}}\right) \right).
	\end{align}
\end{theorem}

\wei{I hided some paragraphs trying to explain the proof here.
	We will re-write a proof outline after revising the proofs.}

\begin{proof} %proof outline of main theorem
	The proof is in Appendix. The main idea is to reduce our analysis to that of CombCascade in \cite{kveton2015combinatorial}. This reduction is challenging for two reasons. First, our setting has contextual information. Second, we consider position-discounted weight $\gamma$.

	Our analysis can be trivially reduced to contextual combinatorial semi-bandits by conditioning on the event of observing all items. Then we can express the expected regret at time $t$ conditioned on the history $\cH_t$ as:
	\begin{align*}
		&\EE[R(t, \bA_t)|\cH_t] \\
		&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right],\\
		&\EE_t[R_{\wedge}(t, \bA_t)] \\
		&\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
	\end{align*}
	and anaylize our problem under the assumption that all items in $\bA_t$ are observed. This reduction might be problematic because the probability $p_{\wedge, t, \bA_t}$ for the conjunctive case can be low.

	Then we use a prefix to replace $\bA_t$ such that the probability of observing all items is close to $f_{\wedge}^{\ast}$ and the gaps are close to those of the original solutions.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}
	Then we need to bound $f(A, \bU_t)$ and $f_{\wedge}(A, \bU_t)$ which is non-linear and contains discounted parameters $\gamma$. First we have the expected reward function is increasing with respect to $w$ when $\gamma~s$ are decreasing and $\gamma's$ are increasing.
	\begin{lemma}
		\CLemmaIncre
	\end{lemma}
	Then we have an estimate of the expected reward with UCB $\bU_t$.
	\begin{lemma}
		\CLemmaTech
	\end{lemma}
	Next we only need to estimate $\det(\bV_t)$ and those contextual information of observed base arms in $\bV$-norms.
	\begin{lemma}
		\CLemmaSumXiEstimateInDet
	\end{lemma}
	\begin{lemma}
		\CLemmaDetVt
	\end{lemma}
	Then it is easy to derive the proof.
\end{proof}

@@

We first provide a basic property of functions $f$ and $f_{\wedge}$ as defined in~Eq.\eqref{eq:functionf} and \eqref{eq:functionfstar}.
\begin{lemma} %lem:increasing
	\label{lem:increasing} 
	\CLemmaIncre
\end{lemma}
\begin{proof}
	Without the loss of generality, we prove for the case of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. First, for $1 \leq k \leq m$, we have
	\begin{align*}
		&\gamma_{k} - \sum_{i=k+1}^m \gamma_i \prod_{j = k + 1}^{i - 1} (1 - w_j') w_i'\\
		\geq &~\gamma_k [1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
		\geq &~\gamma_{k} \cdot 0 = 0.
	\end{align*}
	Then it implies that
	\begin{align*}
		&\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
		\leq &\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'.\\
	\end{align*}
	Therefore, 
	\begin{align*}
		& f(A; w_1, \dots, w_k, w_{k+1}', \dots, w_m')\\
		&=\sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
		&\qquad \cdot [\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
		&\leq \sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
		&\qquad \cdot [\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
		&=f(A; w_1, \ldots, w_{k-1}, w_{k}', \ldots, w_m').
	\end{align*}
	By letting $\gamma_k = 1 - \gamma_k'$ and using the relation in Eq. \eqref{eq:ConDisRelation}, the increasing property of $f_{\wedge}$ is obtained directly.
\end{proof}

The following lemma provides the relationship between an estimated mean vector $w$ and its upper bound vector $u$, in terms of their $f$ function values.
\begin{lemma} %lem:estimateTech
	\label{lem:estimateTech}
	\CLemmaTech
\end{lemma}
\begin{proof}
	We prove this by induction. It holds obviously for $m = 1$.
	\begin{align*}
		&~~f(A^{(m+1)}, u)\\
		&= f(A^{(m)}, u) + \gamma_{m+1}\prod_{k=1}^m(1 - u_k) u_{m+1}\\
		&\leq f(A^{(m)}, u) +  \gamma_{m+1} \prod_{k=1}^m(1 - w_k) (w_{m+1} + r_{m+1})\\
		&\leq f(A^{(m)}, w) + \sum_{k=1}^m \gamma_k r_k \\
		&\qquad + \gamma_{m+1} \prod_{k=1}^m(1 - w_k) w_{m+1} + \gamma_{m+1} r_{m+1}\\
		&= f(A^{(m+1)}, w) + \sum_{k=1}^{m+1} \gamma_k r_k
	\end{align*}
	\begin{align*}
		&~~f_{\wedge}(A^{(m+1)}, u) \\
		&= f_{\wedge}(A^{(m)}, u) -\prod_{k=1}^{m} u_k \\
		&\qquad+ \gamma_{m+1}' (\prod_{k=1}^{m} u_k) (1 - u_{m+1})+ \prod_{k=1}^{m+1} u_k\\
		&= f_{\wedge}(A^{(m)}, u) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} u_k) (1 - u_{m+1})\\
		&\leq f_{\wedge}(A^{(m)}, u) - (1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k) (1 - u_{m+1})\\
		&\leq f_{\wedge}(A^{(m)}, u) -(1 - \gamma_{m+1}') (\prod_{k=1}^{m} w_k)  (1 - w_{m+1} - r_{m+1})\\
		&\leq f_{\wedge}(A^{(m)}, w) +  \sum_{k=1}^{m} (1 - \gamma_k') r_k \\
		&\qquad - (1 - \gamma_{m+1}') (1 - w_{m+1}) \prod_{k=1}^{m} w_k + (1 - \gamma_{m+1}') r_{m+1}\\
		&\leq f_{\wedge}(A^{(m+1)}, w) + \sum_{k=1}^{m+1} (1 - \gamma_k') r_k
	\end{align*}
\end{proof}
